---
title: "Ls1-2 Reading XML"
output: html_document
---

#Reading XML

>XML: Extensible Markup Language

* Frequently used to store structured data
* Particularly widely used in Internet applications
* Extracting XML is the basis for most web scarping
* Components:
  + Markup: labels that give the text structure
  + Connect: the actual text of the document

>Tags, elements and attributes

* Tags correspond to general labels
  + Start tags <section>
  + End tags </section>
  + Empty tags <line-break />
* Elements are specific examples of tags
  + <Greeting> Hello, world </Greeting>
* Attributes are components of the label
  + <step number="3"> Connect A to B. </step>
  
[ XML example ](https://www.w3schools.com/xml/simple.xml)

## Read the file into R
>XML package

```{r}
library(XML)
library(xml2)
fileUrl <- "./simple.xml"
doc<- xmlTreeParse ( fileUrl, isURL = TRUE,useInternalNodes = TRUE)
rootNode<-xmlRoot(doc)
xmlName(rootNode)
```
```{r}
names(rootNode)
rootNode[[1]]
rootNode[[1]][[1]]
```

>XPath

* */node*: Top level node
* *//node*: Node at any level
* *node [@attr-name]*: Node with an attribute name
* *node [@attr-name="bob"]*: Node with attribute name attr-name="bob"

[ Further Info](.\XML.pdf)

```{r}
xpathSApply(rootNode,"//name",xmlValue)
xpathSApply(rootNode,"//price",xmlValue)
```

###Example: Baltimore Ravens

[updates1](https://github.com/lgreski/datasciencectacontent/blob/master/markdown/cleaningData-demystifyingHTMLParsing.md)

```{r}
library(RCurl)
fileUrl <- "https://www.espn.com/nfl/team/_/name/bal/baltimore-ravens" 
xData <- getURL(fileUrl) 
doc <- htmlTreeParse(xData,useInternalNodes = TRUE)
scores<-xpathSApply(doc,"//div[@class='score']",xmlValue)
#div[@class='score']: div items with its class as score
teams <- xpathSApply(doc, "//div[@class='game-info']", xmlValue) 
```

Or using **xml2 package**

```{r}
library(xml2)
suppressWarnings(dx<-read_xml("https://www.espn.com/nfl/team/_/name/bal/baltimore-ravens",
                              as_html=TRUE))
teams<-as.character(xml_contents(xml_find_all(dx,"//div[@class='game-info']")))
scores<-as.character(xml_contents(xml_find_all(dx,"//div[@class='score']")))
```


[updates2](https://github.com/lgreski/datasciencectacontent/blob/master/markdown/cleaningData-demystifyingHTMLParsing.md)

[Baltimore Ravens](https://www.espn.com/nfl/team/_/name/bal/baltimore-ravens)
